---
title: "task3_truenumber"
author: "zby"
date: "12/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F,message = F,echo=F,highlight=F)
library(knitr)
library(gutenbergr)
library(tidyverse)
library(tidytext)
library(magrittr)

```

## MA615 Assignment4 Text Analysis_Task3 

### Introduction of The Cash Boy

The book I choose is The Cash Boy,a juvenile fiction.  Here is the link https://www.gutenberg.org/ebooks/296. I used the gutenbergr package which provides access to the public domain works from Project Gutenberg collection to download this book.

The story is about a little poor boy, which lost everyone he loved except his little sister. Because the situation with no parents and income, the boy moved to New York for himself, so he could make some money for him and his sister.


Installing the R tnum package
```{r cars}
#install.packages("glue")
#install.packages("devtools")
#install.packages(c('devtools','cli'))  package or namespace load failed for ‘devtools’ in loadNamespace(j <- i[[1L]], c(lib.loc, .libPaths()), versionCheck = vI[[j]]):载入了名字空间‘cli’ 3.0.1，但需要的是>= 3.1.0
library(devtools)
devtools::install_github("Truenumbers/tnum/tnum",force = TRUE) 
```


Load the tnum package and authorize the mssp1 server

```{r pressure, echo=FALSE}
library(tnum)
tnum.authorize("mssp1.bu.edu") #connect and authenticate to Truenumbers server
tnum.setSpace("test2") #set a particular numberspace as current
```

I download  The Cash Boy and put it into tnum.

```{r}
source("Book2TN-v6A-1.R")
TCB<-gutenberg_download(gutenberg_id = 296) #Download the book
#TCB_txt<-read_lines("The cash boy.txt")
# write.table(TCB,"The cash boy.txt",row.names=FALSE,col.names=FALSE)
TCB_fix<-read.table("The cash boy.txt",header=T)
#tnBooksFromLines(TCB_fix$text,"TheCashBoy1/ZZzby")
tnum.getDBPathList(taxonomy="subject",levels = 2) #get phrase taxonomies
```

### use query to check INs

I show the tnum database of The Cash Boy.

```{r}
q20<-tnum.query("TheCashBoy1/ZZzby# has *",max=30)
df20<-tnum.objectsToDf(q20)
knitr::kable(df20%>%select(subject:numeric.value)%>%head())

#q22<-tnum.query("TheCashBoy1/ZZzby/headings:0022# has *")
#df22<-tnum.objectsToDf(q22)
#ord_ch1<-unlist(tnum.query("TheCashBoy1/ZZzby/headings:0022# has ordinal"))
```

I use query section and heading text to show the head

```{r}
q20<-tnum.query("TheCashBoy1/ZZzby# has *",max=30)
df20<-tnum.objectsToDf(q20)
df20%>%select(subject:string.value)%>%head()
```


### Sentiment Annalysis

I used sentimentr package to do sentiment analysis and get sentiment score. 

```{r}
library(sentimentr)
df30<- tnum.query("TheCashBoy1/ZZzby/section# has text",max=500) %>% tnum.objectsToDf()
book_sentence<-df30 %>% separate(col=subject,
                  into = c("path1", "path2","section","paragraph","sentence"), 
                  sep = "/", 
                  fill = "right") %>% 
  select(section:string.value)
#detect the section paragraoh and sentence number and convert it from character into numeric
book_sentence<-book_sentence %>% mutate_at(c('section','paragraph','sentence'),~str_extract_all(.,"\\d+") %>% unlist() %>% as.numeric())
# use sentimentr to get sentiment score group by these scores with section to get the average result
sentence_out<-book_sentence %>% dplyr::mutate(sentence_split = get_sentences(string.value)) %$%
    sentiment_by(sentence_split, list(section))
plot(sentence_out)
```


### Comparative Analysis

I used four lexicons to analyze The Cash Boy. Now I have the sentence-level scores, I want to do comparative analysis.

```{r}
tidy_tcb <- TCB %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)


bing <- get_sentiments('bing')
tcb_bing <- inner_join(tidy_tcb, bing) %>% mutate(index = linenumber %/% 80)
index_bing <- tcb_bing %>% group_by(index) %>%
              mutate(whether = ifelse(sentiment == 'positive', 1, -1)) %>% 
              summarize(value = sum(whether))
p1 <- ggplot(data = index_bing, mapping = aes(x=index, y=value)) + geom_col(aes(fill=index), show.legend = F) +
  labs(title='the bing lexicon sentiment scores across the article', x = 'chunks', y = 'score') +
  geom_smooth(se = F, color='orange', size = 1.5)
# do the sentiment analysis using afinn engine
afinn <- get_sentiments('afinn')
tcb_afinn <- inner_join(tidy_tcb, afinn) %>% mutate(index = linenumber %/% 80)
index_afinn <- tcb_afinn %>% group_by(index) %>% summarize(value = sum(value))
p2 <- ggplot(data = index_afinn, mapping = aes(x=index, y=value)) + geom_col(aes(fill=index), show.legend = F) +
  labs(title='the afinn lexicon sentiment scores across the article', x = 'chunks', y = 'score') + 
  geom_smooth(se = F, color='orange', size = 1.5)
```



```{r, echo = F, warning = F, message = F, fig.width = 16, fig.height = 12}
library(grid)
library(gridExtra)
grid.arrange(p1, p2, ncol = 2)
```

According to the above plots, the trend of sentence-level scores and previous sentiment scores are the same. At the begin, Frank lost parents, so he experienced sadness. Sentiment Scores change from positive to negative twice. After Frank arrived New York, he makes some money so that he can support himself and little sister. There are joys and sorrows in New York, so there are positive and negative scores. At the end of sotry, Frank walked out of sorrow, sentiment scores are positive.  

### Extra Credit

Frank is the main character in The Cash Boy. Firstly, I find Frank. Secondly, I calculated the times Frank appeared in each chapter. Finally, I used table to show the section Frank appeared.

```{r}
tcb_sentence<-df30 %>% separate(col=subject,
                  into = c("path1", "path2","section","paragraph","sentence"), 
                  sep = "/", 
                  fill = "right") %>% 
  select(section:string.value)

book_sentence_indi<-tcb_sentence %>% mutate(Frank=str_match(tcb_sentence$string.value,regex('([Ff]rank)'))[,1])
# use sentiment_by to get the score
score<-book_sentence_indi %>% dplyr::mutate(sentence_split = get_sentences(string.value))%$%
    sentiment_by(sentence_split) %>% `$`(ave_sentiment)

book_sentence_indi$score<-score
re<-book_sentence_indi %>% group_by(section) %>% summarise(Frank=sum(Frank %>% is.na() %>% `!`()))
                                                      
knitr::kable(re,'simple')

```

### Reference

Julia Silge & David Robinson. (2016). Welcome to Text Mining with R [online]. Available from: https://www.tidytextmining.com/index.html [accessed 9 December 2021].
